General purpose gene annotation using deep learning

### 2020-01-09 paper/main.tex
metrics

Model evaluation during training was done with a metric that we call the {\it Genic F1}. This score is very similar to a classic F1 score calculated across multiple classes, except that it takes into account that the data is

@@

\subsection{Evaluation of Augustus}
What Marvin did, why we don't use Genic F1 for comparison, etc

>>>>

	We use metrics two metrics to judge model performance. The {\it Genic F1} is our primary metric that provides the most comprehensive picture of annotation quality in one number. The {\it Subgenic F1} is similar to the Genic F1, except that it does not take UTR prediction quality into account. This is done for comparability with Augustus and further explained in chapter \ref{augustus}. Both metrics work by summing up True Positives (TP), False Positives (FP), etc of each considered class before calculating precision, recall and ultimatily a F1 score. Both metrics do also leave out the intergenic class, as this is by far the easiest to predict and could potentially skew the results too far away from the performance in the genic region. The Genic F1 thus essentially provides a weighted mean of the classes UTR, CDS and Intron while the Subgenic F1 sums up only CDS and Intron. All individual class performances are reported in the Suplementary Material (?).

@@

\subsection{Evaluation of Augustus} \label{augustus}
What Marvin did, why we don't use Genic F1 for comparison, etc
